Abb Analysis

### 2017-02-07 abbDataAnalysis_Script.Rmd
Revert "re-working global imputation"
This reverts commit 108f255460ac4503081432f971eb95181152d6f0.

  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
                            as.factor(bedbath) + as.factor(suburb) + 
                            as.factor(ltr.month))

@@

  imp.rents <- imputeRents(ltr.df=ltr.data, 
                           str.df=str.data, 
                           mod.spec=ltr.mod.spec,
                           clip.field='suburb')

  str.glob <- merge(str.data, imp.rents$str, by='property.id')

@@

  # Apply dom to abb
  str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median')

>>>>

  ltr.mod.spec <- formula(log(event.price) ~ as.factor(type) + 
                            as.factor(bedbath) + as.factor(suburb) + 
                            as.factor(ltr.month))
  str.mod.spec <- formula(log(nightly.rate) ~ as.factor(type) + 
                            as.factor(bedbath) + as.factor(suburb))

@@

  imp.data <- imputeRatesRents(ltr.df=ltr.data, 
                               str.df=str.data, 
                               ltr.mod.spec=ltr.mod.spec, 
                               str.mod.spec=str.mod.spec,
                               clip.field='suburb')

From the imputed results, we extract the base data (with imputed values) as well as the model summaries.

  # Extract out DFs (only those that imputed)
  str.imp <- imp.data$str
  ltr.imp <- imp.data$ltr

  # Extract models
  str.sum <- summary(imp.data$str.mod)
  ltr.sum <- summary(imp.data$ltr.mod)

@@

  # Apply dom to abb
  str.imp$imp.dom <- imputeDOM(str.imp, ltr.imp, calc.type='median')

  # Apply occ.rate to ltr
  ltr.imp$imp.occ <- imputeOccRate(ltr.imp, str.imp, calc.type='median')
